Pew Cleaning

### 2021-05-07 code/import_pew_data.Rmd
new stuff

## Initial Data Import
```{r, include=FALSE}
if(!file.exists("../../Pew/pewTech.RData") ) { #skip import if RData file exists
# Data set from Pew 
importedData <- read_sav("../../Pew/ATP W49.sav")

@@

## Additions for KNOW Dummy Var
```{r}
###Generate KNOW Dummy Var###
count_df <- pew %>% mutate(K1T = ifelse(KNOW1_W49 == "Can track your visits and activity on the site", yes = 1, no = 0 ),
               K3T = ifelse(KNOW3_W49 == "Has created a contract between itself and its users about how it will use their data", yes = 1, no = 0),
               K4T = ifelse(KNOW4_W49 == "Information entered into the site is encrypted", yes = 1, no = 0),
               K7T = ifelse(KNOW7_W49 == "Internet service providers should treat all traffic on their networks equally", yes = 1, no = 0),
               K8T = ifelse(KNOW8_W49 == "A coworker who uses the same computer", yes = 1, no = 0),
               K9T = ifelse(KNOW9_W49 == "Picture of 2-step code", yes = 1, no = 0)
               ) %>% select(K1T, K3T, K4T, K7T, K8T, K9T)
# count_df

@@

## Additions for RTBFG Dummy Var
```{r}
# TODO
```

>>>>

## Initial Data Import
```{r generate Rda file, include=FALSE}
if(!file.exists("../../Pew/pewTech.RData") ) { #skip import if RData file exists
# Data set from Pew 
importedData <- read_sav("../../Pew/ATP W49.sav")

@@

## Additions for KNOW Dummy Var
```{r KNOW Dummy Var}
###Generate KNOW Dummy Var###
count_df <- pew %>% mutate(K1T = ifelse(KNOW1_W49 == "Can track your visits and activity on the site", yes = 1, no = 0 ),
               K3T = ifelse(KNOW3_W49 == "Has created a contract between itself and its users about how it will use their data", yes = 1, no = 0),
               K4T = ifelse(KNOW4_W49 == "Information entered into the site is encrypted", yes = 1, no = 0),
               K7T = ifelse(KNOW7_W49 == "Internet service providers should treat all traffic on their networks equally", yes = 1, no = 0),
               K8T = ifelse(KNOW8_W49 == "A coworker who uses the same computer", yes = 1, no = 0),
               K9T = ifelse(KNOW9_W49 == "Picture of 2-step code", yes = 1, no = 0)
               ) %>% select(K1T, K3T, K4T, K7T, K8T, K9T)
# count_df

@@

## Additions for RTBF Dummy Var
```{r RTBF Dummy Var}
count_rtbf <- pew %>% mutate(forget_a = ifelse(RTBFa_W49 == "Yes, should be able to remove this from online searches", yes = 1, no = 0),
                             forget_b = ifelse(RTBFb_W49 == "Yes, should be able to remove this from online searches", yes = 1, no = 0),
                             forget_c = ifelse(RTBFc_W49 == "Yes, should be able to remove this from online searches", yes = 1, no = 0),
                             forget_d = ifelse(RTBFd_W49 == "Yes, should be able to remove this from online searches", yes = 1, no = 0)
                             ) %>% select(forget_a, forget_b, forget_c, forget_d)

## Sum RTBF count dummies, add to pew data set
pew <- pew %>% mutate(sumRTBF = count_rtbf$forget_a + count_rtbf$forget_b + count_rtbf$forget_c + count_rtbf$forget_d,
                      propRTBF = sumRTBF/4,
                      .after = RTBFd_W49)
```
